---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit then `knit` that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sos

<!-- badges: start -->
[![R-CMD-check](https://github.com/sbgraves237/sos/workflows/R-CMD-check/badge.svg)](https://github.com/sbgraves237/sos/actions)
<!-- badges: end -->

The `sos` package provides the fastest literature search I know for anything statistical.  It queries the `RSiteSearch` database and sorts the results by package not just help page.  The package includes a vignette reprinted from [*The R Journal*](https://journal.r-project.org/archive/2009/RJ-2009-017/RJ-2009-017.pdf).  

## Installation

You can install the released version of sos from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sos")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sbgraves237/sos")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(sos)
(PL <- findFn('Petal.Length'))
```

The `print` method for an object of class `findFn`, like `PL`, opens two taps in the default browser:  The first has links to individual help pages sorted by package.  The second is a package summary.  

The current version of `sos` extracts some information only from installed packages.  You can install the leading packages in a search as follows:  

```{r installPkgs}
installPackages(PL)
PL
```

